---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PETDiagnostics

<!-- badges: start -->
<!-- badges: end -->

The goal of PETDiagnostics is to assess feasibility of data sources to perform observational studies on pregnancy related topics using the pregnancy extension tables in OHDSI.

## Installation

You can install the development version of PETDiagnostics like so:

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("oxford-pharmacoepi/PETDiagnostics")
```

## Example
### Create a reference to data in the OMOP CDM format

The PETDiagnostics package is designed to work with data in the OMOP CDM format, so our first step is to create a reference to the data using the CDMConnector package. Here we´ll generate an example reference with simulated data (to see how you would create a reference to your database please consult the CDMConnector package documentation).

```{r example}
library(PETDiagnostics)
library(CDMConnector)
library(dplyr)


# We first need to create a mock database with a cdm reference
# this function creates a mothertable and a babytable
cdm<-mockPregnancy(mothertable = NULL,
                          babytable = NULL,
                          pregnancy_size = 100,
                          fetus_size = 110,
                          seed = 1)

# this is what the table(s) look like
# use the mothertable and/or the babytable depending on your data
head(cdm$mothertable)
head(cdm$babytable)
```

## Execute the diagnostic checks of your table(s)
### if both tables are available, all checks are possible
### if only the mothertable is available, the "fetusid" and "weightDist" check is not possible, put babytable = NULL
### if only the babytable is available, only the "overview", "missing", "weightDist", and "bitSet" check is possible, put mothertable = NULL


```{r}
resultList <- executeChecks (
                          mothertable = cdm$mothertable,               
                          babytable = cdm$babytable,                  
                          checks = c("overview","annualOverview","missing", "unknown","gestationalAge","datesAgeDist","outcomeMode",
                                     "fetusesLiveborn","fetusid","weightDist","bitSet"),                       
                          minCellCount = 5,
                          minGestAge_Days = 21,
                          verbose = FALSE)
```
## Exporting results
### resultList is the named list with results
### databaseId is the database identifier
### outputFolder is the folder to write to

```{r}
writeResultToDisk (resultList = resultList, databaseId = "mock", outputFolder = tempdir())
```

```{r, echo=FALSE}
  DBI::dbDisconnect(attr(cdm, "dbcon"), shutdown = TRUE)
```
