---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PETDiagnostics)
library(CDMConnector)
library(dplyr)
library(DT)
```

Here we use the mockdata for training purposes. 
But ideally, you use your real data, so just connect to your database (if you are not already connected). 
The idea would be to name these new cdm tables in the future motherTable and babyTable.

```{r}
cdm <-  PETDiagnostics:::mockPregnancy(motherTable = NULL,
                          babyTable = NULL,
                          pregnancy_size = 100,
                          fetus_size = 110,
                          seed = 1)
```

We can run all available checks at the same time using the ´executeChecks()´ function. This will return a list which contains the results of each check.

```{r eval=FALSE}
executeChecks (
  motherTable = cdm$motherTable,  
  babyTable = cdm$babyTable,                  
  checks = c("overview","annualOverview","missing", "unknown","gestationalAge","datesAgeDist","outcomeMode",
                                     "fetusesLiveborn","fetusid","weightDist","bitSet"),                       
  minCellCount = 5,
  minGestAge_Days = 21,
  verbose = FALSE)
```

The`cdm` is the database reference of the OMOP CDM using the `CDMConnector` package.\
The `motherTable` is the `motherTable` in the CDM. The `babyTable` is the `babyTable` in the CDM. `checks` allows to select the checks to be executed, by default, all the checks will be run. The `minCellCount` is minimum number of events to report, numbers lower than this will be obscured. The number zero will not be obscured´, `minGestAge_Days` implies the number of minimum number of gestational age that may be the minimum for pregnancies to be recorded. 

```{r executeChecks}
resultList<-executeChecks(motherTable = cdm$motherTable,               
                          babyTable = cdm$babyTable)
```

We can then check what results available from ´executeChecks()´ by

```{r}
names(resultList)
```

Let's take a look at the results. the missingSummaryMother contains all the variables, their count of missings, and the proportion in relation to all pregnancies recorded in the motherTable.

```{r,  message=FALSE }
DT::datatable(resultList$missingSummaryMother,
  rownames = FALSE
)
```

After running the checks, we can write the CSV files into a zip file to disk using the `writeResultToDisk()` function.

```{r eval=FALSE}
writeResultToDisk(resultList=resultList,
                  databaseId = "your_database_id", 
                  outputFolder = tempdir())
```

```{r, echo=FALSE}
  DBI::dbDisconnect(attr(cdm, "dbcon"), shutdown = TRUE)
```
